\section*{3/9}
  \subsection*{Pythagorean triples and Fermat's last theorem}
    The solution: $x = m^2 - n^2$, $y = 2mn$, $z = m^2 + n^2$, $gcd(m,n) = 1$,
    $m$ and $n$ are not both odd, and $gcd(x,y) = 1$.\\\\
    If $d | m, n$, then let $m' = \frac{m}{d}$, $n' = \frac{n}{d}$, $x' = 
    \frac{x}{d^2}$, $y' = \frac{y}{d^2}$, and $z' = \frac{z}{d^2}$.\\\\
    If $m, n$ are both odd, $m' = \frac{m+n}{2}$, $n' = \frac{m-n}{2}$,
    $x' = \pm \frac{y}{2}$, $y' = \pm \frac{x}{2}$, and $z' = \frac{z}{2}$.\\
    Suggestive alternate formula:\\
    $$
      x + iy = (m + in)^2
    $$
    $$
      z = |m + in|^2 = (m+in)(m-in)
    $$
    Official (lame) full solution:\\
    $$
      x = k(m^2 - n^2), y = 2kmn, z = k(m^2 + n^2)
    $$
    Another proof:
    \begin{proof}
      $x^2 + y^2 = z^2$ is a homogenous Diophantine equations.\\
      Solutions in $\mathbb{Z} \leftrightarrow $ solutions in $\mathbb{Q} 
        \leftrightarrow$ solutions to $x^2 + y^2 = 1$.
    \end{proof}
  \subsection*{Open Problem}
    Are $\mathbb{Q}$ Diophantine equations computationally universal and/or
    mathematically universal? (like $\mathbb{Z}$ diophantine equations are)\\\\
    \underline{Example}: 
    \begin{eqnarray*}
      x^2 + y^2 = z^2  &\leftrightarrow& x^2 + y^2 = 1\\
      3^2 + 4^2 = 5^2  &\leftrightarrow& \left(\frac{3}{5}\right)^2 + \left(
        \frac{4}{5}\right)^2 = 1
    \end{eqnarray*}
    What is the solution to $x^2 + y^2 = 1$? A unit circle centered at the
    origin.\\
    Suppose that $x$ and $y$ are rational. Suppose I form a line between 
    $(0,1)$ and $(x,y)$, is the slope of the line rational? Yes! In fact,
    the slope, $s$, is $\frac{y-1}{x}$.\\\\
    If $s \in \mathbb{Q}$, then $(x,y) \in \mathbb{Q}^2$ because you have
    a quadratic equation such that one solution, $(0,1)$, is rational.\\
    $x^2 + y^2 = 1$ and $y = xs + 1$, so \\
    $x^2 + (sx + 1)^2 = 1$, $x^2 + s^2x^2 + 2sx + 1 = 1$\\
    We then have $(1 + s^2)x + 2s = 0$, so $x = \frac{-2s}{1+s^2}$.\\
    Then, $y = sx + 1 = \frac{1 - s^2}{1 + s^2}$.\\
    Let $s = \frac{n}{m}$, then $x = \frac{-2mn}{n^2 + m^2}$ and $y = \frac{
    m^2 - n^2}{m^2 + n^2}$. Although a few cosmetic errors, we can fix it
    to look like what we're looking for.\\\\
    This is the same idea that works for any diophantine equations. with any 
    quadratic(x,y,z) = 0, which is homogenous and such that you know one 
    solution.\\
    \underline{Example}: $3x^2 + 4y^2 = 7z^2$. A solution, $(1,1,1)$ and
    this is homogenous since all the terms are quadratic.\\
    $3x^2 + 4y^2 = 7$ forms the ellipse. $s \in \mathbb{Q} \leftrightarrow
    (x,y) \in \mathbb{Q}^2$.\\\\
  \subsection*{A case of Fermat's last theorem}
    $x^4 + y^4 = z^4$ has a no non-trivial solutions. Proved by 
    "infinite descent." Solution $\Rightarrow$ a smaller solution. This is
    a contradiciton with a form of induction.\\\\
    What we actually show by induction is $x^4 + y^4 = z^2$ and $4yx^4 +
    y^2 = z^4$ have no solutions.\\
